Consistent Polyhedral Surrogates via Embedding

### 2019-05-20 notes/jessie-proof-sketches.tex
more proof comments

  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  Call the set of full-dimensional cells in this power diagram $\F$, and note that $\F$ is finite since it defined by a projection of a polyhedral function.
  \raf{I would have thought we could use COLT Prop 12 at this point in the proof...}
  For each $f \in \F$, choose some $p \in \inter{f}$ and add some $u_f \in \argmin_u L(u, p)$ to the set $\R$.
  As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$ \raf{how does this follow from closure?}.
  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 
  Thus, $L$ embeds a discrete loss-- namely, $L|_\R$.
\end{proof}
%\hrulefill
%\begin{proof}[Non-property version]
%  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
%  Therefore, $\risk{L}$ is polyhedral.
%
%  For the reverse implication, suppose $\risk{L}$ is polyhedral.
%  For each facet $f \in F$, consider the report $u_f$ as constructed above.
%  Since $F$ is finite, the set $\R = \{u_f\}_{f \in F}$ is finite.
%  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
%
%  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
%  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
%  For all $p \in \simplex$, we observe
%  \begin{align*}
%  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
%  \end{align*}
%  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
%  Thus, $L$ embeds the discrete $\ell$ as constructed by Proposition~\ref{prop:embed-bayes-risks}.
%
%  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
%\end{proof}
%\hrule 
\hrulefill

>>>>

  Now suppose $\risk{L}$ is polyhedral, and $\Gamma := \prop{L}$.
  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  Call the set of full-dimensional cells in this power diagram $\F$, and note that $\F$ is finite since it defined by a projection of a polyhedral function.
  \raf{I would have thought we could use COLT Prop 12 at this point in the proof... take a look at its proof, the 2 $\Rightarrow$ 3 part, and note that it already invokes Lemma 11, so it already proves this direction}
  For each $f \in \F$, choose some $p \in \inter{f}$ and add some $u_f \in \argmin_u L(u, p)$ to the set $\R$.
  As level sets are closed, we know that $\Gamma(p) \cap \R$ is nonempty for all $p \in \simplex$ \raf{how does this follow from closure?}.
  By \jessie{COLT Lemma 11}, we know $\Gamma$ embeds $\Gamma \cap \R$ elicited by the discrete loss $L|_\R$. 
  Thus, $L$ embeds a discrete loss-- namely, $L|_\R$.
\end{proof}
%\hrulefill
%\begin{proof}[Non-property version]
%  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
%  Therefore, $\risk{L}$ is polyhedral.
%
%  For the reverse implication, suppose $\risk{L}$ is polyhedral.
%  For each facet $f \in F$, consider the report $u_f$ as constructed above.
%  Since $F$ is finite, the set $\R = \{u_f\}_{f \in F}$ is finite.
%  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
%
%  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
%  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
%  For all $p \in \simplex$, we observe
%  \begin{align*}
%  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
%  \end{align*}
%  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
%  Thus, $L$ embeds the discrete $\ell$ as constructed by Proposition~\ref{prop:embed-bayes-risks}.
%
%  \raf{Just take the discrete reports to be the facets, and use the Bayes risk result.}
%\end{proof}
%\hrule 
\hrulefill
